---
title: "R-Squared"
description: |
author:
  - name: Zy;Keyah Horn
date: 2021-12-04
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

1\. *R-squared does not measure goodness of fit. It can be arbitrarily low when the model is completely correct*

I found this interesting because originally I thought that R-squared measured goodness of fit. R-squared is a statistical measure of how close the data are to the fitted regression line. You can have a low R-squared value for a good model, or a high R-squared value for a model that does not fit the data.

```{r}
r2.0 <- function(sig){
  # our predictor
  x <- seq(1,10,length.out = 100)   
  # our response; a function of x plus some random noise
  y <- 2 + 1.2*x + rnorm(100,0,sd = sig) 
  # print the R-squared value
  summary(lm(y ~ x))$r.squared          
}

sigmas <- seq(0.5,20,length.out = 20)
 # apply our function to a series of sigma values
rout <- sapply(sigmas, r2.0)            
plot(rout ~ sigmas, type="b")

```

R-squared tanks hard with increasing sigma, even though the model is *completely correct* in every respect.

R-squared is always between 0 and 100%. 0% indicates that the model explains none of the variability of the response data around its mean. 100% indicates that the model explains all the variability of the response data around its mean. The higher the R-squared, the better the model fits your data.
